

\documentclass{report}
\usepackage{fontspec}
\newfontfamily
\arabicfont{Al Nile}
\setlength{\parindent}{0pt}
\setlength{\parskip}{8pt plus3pt minus2pt}
\raggedright

\begin{document}

\newcommand{\mnote}[1] {\marginpar{\scriptsize \raggedright #1 }}


	\chapter{Diary 53\ \\}

	\marginpar{}

	\par{
 	DIARY, Nr 53\ \\1902/3\ \\\ \\
	}

	\begin{tabular}{|c|c|c|c|c|}
	\hline
	
	\hline
	\end{tabular}

	\\
The country house valued at
	&
1500
	&

	\\
in the arac business I have put in all
	&
2500
	&
\ \\
	\marginpar{
	\arabicfont 1ا3ليوم نيسان ليلاً اكتب. قرأت هذا الدفتر في نادي السعدون واتممت هذه (؟) 2فلا حاجة الى الرجوع فأن الحواشي مهيأة لآدخل المواد في الفهارس
  \[p: 2 \]
}

	\marginpar{1902 Jany}

	\marginpar{Supposed Plague in Baghdad quarantine established}

	\marginpar{24 Frid The 6.46}

	\par{
 	From Diary No. 52\ \\
	}

	\par{
 	Light N.W. breeze \& cloudy;\ \\I feel better \& stronger today \& have\ \\much appetite; I got some boiled\ \\Biz fish for breakfast, which I\ \\found very delicious; I also took\ \\some Arrow root etc; \~{} But I feel\ \\so thursty always, \& only like to\ \\suck sweet Lemon or Oranges;\ \\
	}

	\par{
 	The Quarantine Authorities\ \\after having inspected the Jewish\ \\quarters with the Turkish Beledyeh\ \\Doctors \& referred the matter\ \\to Constanple, a decision came\ \\to establish a Cordon around\ \\Baghdad of 5 days quarantine\ \\on all those that leave the town\ \\and consequently, a quarantine\ \\been put yesterday at Gherara,\ \\Khan Beni Saad, Mahmoodieh,\ \\Salahieh etc etc; The Steamers\ \\will also have to make 5 days\ \\quarantine at \lbrack strikethrough "Diala"\rbrack Gherara\ \\
  \[p: 3 \]

	}

	\marginpar{1902 Jany}

	\marginpar{
	\arabicfont 1بالو عند ريشارز3 بمناسبة2 ميلاد امبراطور المانية}

	\par{
 	and the other doctors disagreed\ \\with the two Beledyeh doctors,\ \\and they do not believe that the\ \\sickness among the Jews is\ \\a real Plague; because the\ \\desease does not resemble each\ \\other, some die suddenly, other get\ \\buboes \& fever \& so on \~{}\ \\
	}

	\par{
 	Mr. Rappaport called to see me,\ \\he was glad to find me getting\ \\better; as on Monday the 27th\ \\is the Emperor of Germany’s\ \\Birthday; Mr. Richarz the consul\ \\is giving a Ball \& supper and\ \\50 persons are invited among\ \\whom my niece Alice, also\ \\Antone Marine his wife and\ \\two daughters; Mr. Richarz\ \\has asked Mr. Rappaport to\ \\see me and to find out if he can\ \\invite my son Alexander and\ \\his wife Mary, \& there will be\ \\no objection on account of us\ \\being in mourning; We told him\ \\that they can go if they like, so he\ \\gave the letter of invitation from\ \\Mr. Richarz;\~{}\ \\
  \[p: 4 \]

	}

	\marginpar{1902 Jany}

	\marginpar{
	\arabicfont ولادة امبراطورالمانية.}

	\marginpar{
	\arabicfont الوالي نامق پـاشا وكاظم پـاشا}

	\par{
 	Light N.W. \& very fine cold\ \\\& freezing; I feel much better,\ \\Took my milk \& a boiled egg;\ \\
	}

	\marginpar{27 Mond The 6.32}

	\par{
 	Today is the birthday of the\ \\Emperor of Germany William the\ \\2d, Official reception is giving\ \\Mr. Richarz the Consul from\ \\10 till 11 AM, I sent Alexander\ \\to visit, there was the Turkish\ \\Band playing, \& all officials\ \\calling; also the Wali Namik\ \\Pasha, Kadem Pasha the acting\ \\Commander in Chief \& all the\ \\foreign consuls \~{}\ \\
	}

	\par{
 	It is very cold again today,\ \\I went out to the other room\ \\sister Medula called, also\ \\the french Priests \& Johny\ \\Pahlawan\~{}\ \\
	}

	\par{
 	Today died Tooza bint\ \\Seman widow of Mr. Johnstone\ \\formerly Quarter Master of the\ \\S.S. Comet, also Attyeh son of\ \\Antone Gorgi from parrelitic\ \\attack\~{}\ \\
	}

	\par{
 	At 9 ½ P.M. Alexander \& his wife\ \\went to the dancing evening given\ \\
  \[p: 8 \]

	}

 
 \end{document}

